A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-03 paper/main.tex
adjust caption of group results figure

\todo{“partial brain coverage” / FoV. MIH: Could become an issue. In the data
paper we showed the coverage. Maybe just ref the figure. CH: gonna take a look how I can adjust the script to get a FoV mask from the data and use it during plotting; otherwise: ref to paper}
\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figures/slicescolorbars}
  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected; MNI template space)}.
\label{fig:results}
\end{figure*}

>>>>

\todo{manually edit/merge slices.svg and colorbars.svg for final slicescolorbars}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/slicescolorbars}
    \caption{Mixed-effects group-level (N=14) GLM contrasts for the
        audio-description of the movie Forrest Gump. Significant clusters
        (Z>3.4, p<0.05 cluster-corrected) are overlaid on the custom T2* EPI
        group template (gray; taken from \citep{hanke2014audiomovie}) which is
    aligned to and overlaid on the MNI152 T1-weighted head template (copper).}
    \label{fig:results} \end{figure*}
